Program Transformations for miniKanren

### 2020-07-10 papers/aplas/text/nonconj.tex
Final

In this approach, we decided not to generalize in the same fashion as CPD or supercompilation.
Our conjunctions are always split into individual calls and are joined back together only if it is sensible.
If the need for generalization arises, i.e. homeomorphic embedding of conjunctions~\cite{de1999conjunctive} is detected, then we immediately stop driving this conjunction (line 12).
When residualizing such a conjunction, we just generate a conjunction of calls to the input program before specialization.

>>>>

In this approach, we do not generalize in the same fashion as CPD or supercompilation.
Our conjunctions are always split into individual calls and are joined back together only if it is meaningful.
If the need for generalization arises, i.e. homeomorphic embedding of conjunctions~\cite{de1999conjunctive} is detected, then we immediately stop driving this conjunction (line 12).
When residualizing such a conjunction, we just generate a conjunction of calls to the input program before specialization.
